Computable Poincar\'e--Friedrichs constants for the $L^{p}$ de~Rham complex over convex domains and domains with shellable triangulations

### 2024-12-18 main.tex
correction

        Once again, $h_{z}$ denotes the height of $z_{S'}$ within $G$.
        Here, we let $Q \subseteq G \cap G^{c}$ be the subsimplex 
        that is complementary to the line segment from the origin to $z_{S'}$ in $G$.
        Equivalently, $Q$ is complementary to the line segment from the origin to $-z_{S'}$ in $G^{c}$.
        From the definition of simplices, we now conclude that any $x \in G \cup G^{c}$ 
        has a unique representation
        \begin{align*}
            x = \lambda z_{S'} + \mu x_{Q}, \quad \lambda \in [-1,1], \quad \mu \in [0,1], \quad |\lambda| + \mu \leq 1, \quad x_{Q} \in Q,
        \end{align*}
        Since $\mu x_{Q}$ lies in the hyperplane spanned by the origin and $Q$, we have 
        \begin{align*}
            \lambda = \lambda(x) := \frac{\langle h_{z},x\rangle}{\langle h_{z},z_{S'}\rangle} 
            .
        \end{align*}
        Based on that observation, we define 
        \begin{align*}
            \Phi_{G}(x) % TODO : Sign error. Check values for 0 and 1. Then proceed from there ... 
            &
            := 
            \mu x_{Q} + \frac 1 2 \left( \lambda(x) - 1 \right) z_{S'}
            \\&
            = 
            x - \lambda(x) z_{S'} + \frac{ \lambda(x)}{ 2 } z_{S'} - \frac{ 1 }{ 2 } z_{S'}
            \\&
            = 
            x - \frac{ \lambda(x) }{2} z_{S'} - \frac{ 1 }{ 2 } z_{S'}
            \\&
            = 
            x - \frac{\langle h_{z},x\rangle}{2\langle h_{z},z_{S'}\rangle} z_{S'} - \frac 1 2 z_{S'}
            .
        \end{align*}
        We readily verify that this transformation is a bi-Lipschitz mapping from $G \cup G^{c}$ onto $G^{c}$
        that satisfies the desired mapping properties. 
        It remains to analyze its Jacobian to get explicit estimates.

@@

            \frac{1}{ 2 \langle h_{z},z_{S'}\rangle }  

@@

            \frac{1}{ 2 \langle h_{z}, h_{z}\rangle } 

@@

            \frac{1}{ 2 } 

@@

            \frac{ 1 \vecnorm{ b_{z} } }{ 2 \vecnorm{ h_{z} } } 

@@

        The Jacobian acts as the identity over the orthogonal complement of the span of $h_{z}$ and $z_{s'}$.

@@

        Hence, $\tan(\beta) = \vecnorm{ b_{z} } / \vecnorm{ h_{z} }$. 
            \Jacobian \Phi_{G}(x) \cdot \hat b_{z} = \hat b_{z},
            \Jacobian \Phi_{G}(x) \cdot \hat h_{z} = \frac 1 2 h_{z} - \frac{ 1 \vecnorm{ b_{z} } }{ 2 \vecnorm{ h_{z} } } \hat b_{z}
        It remains to study the singular values of the matrix 

@@

                 \frac 1 2             & 0 
                -\frac 1 2 \tan(\beta) & 1 

@@

            \frac{1}{4} \sqrt{ 9 + \tan(\beta)^2 } + \frac{1}{4} \sqrt{ 1 + \tan(\beta)^2 } 

@@

            \frac{1}{4} \sqrt{ 9 + \tan(\beta)^2 } - \frac{1}{4} \sqrt{ 1 + \tan(\beta)^2 } 

@@

            \frac 1 4 \sqrt{ 9 + (\ell+1)^2 \aspectratio(T)^2 } + \frac 1 4 \sqrt{ 1 + (\ell+1)^2 \aspectratio(T)^2 }
            1 + \frac{1}{2} (\ell+1) \aspectratio(T) 

@@

            \frac 1 2 \sqrt{ 9 + (\ell+1)^2 \aspectratio(T)^2 } + \frac 1 2 \sqrt{ 1 + (\ell+1)^2 \aspectratio(T)^2 }
            2 + (\ell+1) \aspectratio(T) 

@@

        \color{red}Moreover, it is evident that the eigenvalues of the Jacobian are $1$ with multiplicity $n-1$ and $\tfrac 1 2$ with multiplicity $1$.\color{black}

@@

            \left( 1 + \frac{1}{2} (\ell+1) \aspectratio(T) \right)

@@

            \left( 2 + (\ell+1) \aspectratio(T) \right)

@@

            \left( 1 + \frac 1 2 ( \ell+1 )\aspectratio(\calT) \right)

@@

            \left( 2 + ( \ell+1 )\aspectratio(\calT) \right)

@@

\begin{remark}\label{remark:improved_starreflection}
    The estimates in Proposition~\ref{proposition:starreflection} should be considered as \textit{proof-of-concept} but not as optimal in any sense.
    Some improvements are immediately possible if $\ell=n-1$. 
    Then the reflection $\Xi$ in Lemma~\ref{lemma:volumecomparison} satisfies the same properties as the mapping $\Xi_{1}$,
    mapping the simplex $T$ bijectively onto the $\Makoto$ and being the identity along the common face $S$.
    However, at any point, the singular values $\sigma_1 \geq \dots \geq \sigma_n$ of the Jacobian of $\Xi$ satisfy 
    %     \begin{gather*}
    %         \sigma_1      \leq \aspectratio(\calT) ( 1 + \diameterratio(\calT) ),
    %         \quad 
    %         \sigma_2,\dots,\sigma_{n-1} \leq 1,
    %         \quad 
    %         \sigma^{-1}_n \leq \aspectratio(\calT) ( 1 + \diameterratio(\calT) ),
    %         \\ 
    %         | \det\Jacobian\Xi^{  } |      \leq \aspectratio(\calT) \diameterratio(\calT),
    %         \quad 
    %         | \det\Jacobian\Xi^{-1} |      \leq \aspectratio(\calT) \diameterratio(\calT).
    %     \end{gather*}
    \begin{gather*} 
        | \det\Jacobian\Xi^{  } |      \leq \aspectratio(\calT) \diameterratio(\calT),
        \quad 
        | \det\Jacobian\Xi^{-1} |      \leq \aspectratio(\calT) \diameterratio(\calT),
        \\
        \sigma_{1}, \sigma_{n}^{-1}
        %&
        \leq 
        \frac{1}{2} 
        %\left( \sqrt{ (1 + a)^2 + c^2 } \pm \sqrt{ (1 - a)^2 + c^2 } \right)
        \sqrt{ \left( \diameterratio(\calT) \aspectratio(\calT) + 1 \right)^{2} + \aspectratio(\calT)^{2} }
        +
        \frac{1}{2} 
        \sqrt{ \left( \diameterratio(\calT) \aspectratio(\calT) - 1 \right)^{2} + \aspectratio(\calT)^{2} }
        ,
        \\
        \sigma_2,\dots,\sigma_{n-1} \leq 1.
        %         \det(\Jacobian \Xi) &\leq \diameterratio(\calT) \aspectratio(T_2)
    \end{gather*}
    These estimates improve over the ones in Proposition~\ref{proposition:starreflection} when the reflection is over a single face.
    We believe that better estimates can be computed from the geometric data also in the other cases.
\end{remark}

\begin{proof}\color{magenta}
    We derive the estimate in several steps. 
    In what follows, we use the notation $\hat z$ for the normalization of any vector $z \in \bbR^{n}$.
    \begin{itemize}
        \item 
        Without loss of generality, after shifting the coordinate system, the barycenter $z_{S}$ of $S$ is the origin.

        We fix the subsimplex $S' \subseteq T$ that is complementary to $S$ within the simplex $T$.
        Note that ${\Gamma_2} \subseteq \partial T$ is the union of exactly those faces of $T$ that contain $S'$,
        whereas ${\Gamma_1} = \Makoto \cap T$ is the union of exactly those faces of $T$ that contain $S$. 
        We let $z_{S'}$ be the midpoint of $S'$.

        We apply barycentric refinement to the simplex $S$ and then the complementary simplex $S'$.
        This produces a triangulation $\calG$ of $\underlying{|T|}$ whose $n$-dimensional simplices contain the vertices $z_{S} = 0$ and $z_{S'}$.

        \item 
        There exists $\varrho > 0$ such that $\patch_{\calT}(S)$ is star-shaped with respect to the closed ball $\overline{\Ball_{\varrho}(z_S)}$.
        % TODO: prove this observation

        Let us write $\rho = \min(1,\varrho)$. 
        We define $y = - \rho \hat z_{S'}$ as vector in the opposite direction of $z_{S'}$ and with length $\rho$. 
        By construction, the closed line segment from $z_{S}$ to $y$ is contained in $\overline{\Ball_{\varrho}(z_S)}$,
        and we conclude that the convex closure of $T$ and $y$ must lie in $\patch_{\calT}(S)$.

        We define another triangulation $\calG^{c}$ as follows:
        given any $n$-simplex $G \in \calG$, 
        we replace its vertex $z_{S}'$ by the vertex $y$ at the opposite position,
        thus obtaining a new $n$-simplex $G^{c}$. 
        Indeed, that $\calG^c$ is a simplicial complex follows easily from $\calD$ being a simplicial complex.

        We let the simplicial complex $\calG^\ast$ be the union of $\calG$ and $\calG^c$. 
        By construction, all its $n$-simplices contain $z_{S}$ as a subsimplex, which is an inner vertex of that triangulation. 
        In particular, $\calD^\ast$ is its own star around $z_{S}$.
        We then define the piecewise affine mapping 
            \Theta_{|G} := A_{G^{c}} \circ A_{G}^{-1}.
        It follows that 
            |\det( \Jacobian      \Theta_{|G} )| = \frac{\vol(G^{c})}{\vol(G)}
        We want to further characterize the singular values of this transform. 
            (1+\rho) \frac{\langle \hat h_{z}, x \rangle}{\langle \hat h_{z}, \hat z_{S'} \rangle}
        Indeed, the right-hand side equals $x$ whenever $x$ lies in the plane orthogonal to $h_{z}$,
        and when $x = z_{S'}$, then 
            y 
            z_{S'}
            (1+\rho) \hat z_{S'} \frac{\langle \hat h_{z}, z_{S'} \rangle}{\langle \hat h_{z}, \hat z_{S'} \rangle}
            z_{S'}
            (1+\rho) \hat z_{S'} \vecnorm{z_{S'}}
            - z_{S'}
            (1+\rho) \frac{\langle h_{z}, h_{z} \rangle}{\langle h_{z}, z_{S'} \rangle} z_{S'}
            (1+\rho) \frac{\langle h_{z}, z_{S'} \rangle}{\langle h_{z}, z_{S'} \rangle} z_{S'}
            (1+\rho) z_{S'}
            - \rho h_{z}
            (1+\rho) b_{z}
            -\rho                                         & 0
            -(1+\rho) \vecnorm{ b_{z} }/\vecnorm{ h_{z} } & 1
            -\rho                 & 0
            -(1+\rho) \tan(\beta) & 1
        Its two singular values are:
            \sigma_{\max}(\Theta,G) 
            \frac 1 2 \sqrt{ \left( 1 + \rho \right)^{2} + (1+\rho)^{2} \tan(\beta)^{2} } + \frac 1 2 \sqrt{ \left( 1 - \rho \right)^{2} + (1+\rho)^{2} \tan(\beta)^{2} }
            \label{math:theta_max}
            \sigma_{\min}(\Theta,G) 
            \frac 1 2 \sqrt{ \left( 1 + \rho \right)^{2} + (1+\rho)^{2} \tan(\beta)^{2} } - \frac 1 2 \sqrt{ \left( 1 - \rho \right)^{2} + (1+\rho)^{2} \tan(\beta)^{2} }
            \label{math:theta_min}
        All other singular values of $\Jacobian\Theta_{|G}$ equal $1$. 
        The singular value $\sigma_{\max}(\Theta,G) \geq 1$ is monotonically increasing in $\tan(\beta)$ and must hence be the maximal singular value of $\Jacobian\Theta_{|G}$.
        Moreover, $\sigma_{\min}(\Theta,G) = \rho / \sigma_{\max}(\Theta,G) \leq \rho \leq 1$ must be the smallest singular value of $\Jacobian\Theta_{|G}$.
        It is evident that $\rho = \vol(G^{c}) / \vol(G)$.

        We develop explicit bounds for these singular values. 
        The definition of the tangent and the decomposition $z_{S'} = h_{z} + b_{z}$ 
        imply that $\tan(\beta) = \vecnorm{ b_{z} } / \vecnorm{ h_{z} }$.

        Recall that $G \in \calG$ is obtained from $T$ via barycentric subdivisions, first at $z_{S}$ and then at $z_{S'}$. 
        Let $F_{z} \subseteq G$ be the face opposite to the vertex $z_{S'}$,
        which must be contained in some face of $T$. 
        Since $S'$ has dimension $n-\ell-1$, the vector $(n-\ell) h_{z}$ is the height vector of that face of $T$. 
        Thus, 
        \begin{align*}
            \frac{ \vecnorm{ b_{z} } }{ \vecnorm{ h_{z} } }
            = 
            \frac{ \vecnorm{ b_{z} } }{ (n-\ell)^{-1} \| (n-\ell) h_{z} \| }
            = 
            \frac{ \vecnorm{ z_{S'} } }{ (n-\ell)^{-1} \| (n-\ell) h_{z} \| }
            \leq 
            (n-\ell) \aspectratio(T)
%             = 
%             \frac{ \vecnorm{ b_{z} } \vol(F_{z}) }{ (n-\ell)^{-1} n \vol(T) }
%             \leq 
%             \frac{ n-\ell }{n!}
%             \cdot 
%             \frac{ \diam(T)^{n} }{ \vol(T) }
            .
        \end{align*}
        We abbreviate 
        \begin{align}\label{math:upper_bound_for_theta}
            \mu_{T,\ell} 
            := 
            \frac 1 2 \sqrt{ \left( 1 + \rho \right)^{2} + (1+\rho)^{2} (n-\ell)^{2} \aspectratio(T)^{2} } 
            + 
            \frac 1 2 \sqrt{ \left( 1 - \rho \right)^{2} + (1+\rho)^{2} (n-\ell)^{2} \aspectratio(T)^{2} }
            .
        \end{align}
        This establishes bounds on the singular values of the transformation. 
        In summary, the singular values of the Jacobian of $\Theta$ at almost every $x$ satisfy 
        \begin{align}
            \sigma_{1}(\Theta,x) \leq \mu_{T,\ell},
            \quad 
            \sigma_{2}(\Theta,x) = \dots = \sigma_{n-1}(\Theta) = 1,
            \quad 
            \sigma_{n}(\Theta,x)^{-1} \leq \mu_{T,\ell} / \rho.
        \end{align}

        Once again, $h_{z}$ denotes the height of $z_{S'}$ within $G$.
        Here, we let $Q \subseteq G \cap G^{c}$ be the subsimplex 
        that is complementary to the line segment from the origin to $z_{S'}$ in $G$.
        Equivalently, $Q$ is complementary to the line segment from the origin to $y$ in $G^{c}$.
        From the definition of simplices, we now conclude that any $x \in G \cup G^{c}$ 
        has a unique representation
        \begin{align*}
            x = \lambda z_{S'} + \mu x_{Q}, \quad \lambda \in [-\rho,1], \quad \mu \in [0,1], \quad |\lambda| + \mu \leq 1, \quad x_{Q} \in Q,
        \end{align*}
        Since $\mu x_{Q}$ lies in the hyperplane spanned by the origin and $Q$, we have 
        \begin{align*}
            \lambda = \lambda(x) := \frac{\langle h_{z},x\rangle}{\langle h_{z},z_{S'}\rangle} 
            .
        \end{align*}
        Based on that observation, we define 
        \begin{align*}
            \Phi_{G}(x) 
            &
            := 
            \mu x_{Q} + \frac{\rho}{\rho+1} \left( \lambda(x) - 1 \right) z_{S'}
            \\&
            = 
            \mu x_{Q} + \frac{\rho}{\rho+1} \lambda(x) z_{S'} - \frac{\rho}{\rho+1} z_{S'}
            \\&
            = 
            x - \frac{\rho+1}{\rho+1} \lambda(x) z_{S'} + \frac{\rho}{\rho+1} \lambda(x) z_{S'} - \frac{\rho}{\rho+1} z_{S'}
            \\&
            = 
            x - \frac{1}{\rho+1} \lambda(x) z_{S'} - \frac{\rho}{\rho+1} z_{S'}
            \\&
            = 
            x - \frac{1}{\rho+1} \frac{\langle h_{z},x\rangle}{\langle h_{z},z_{S'}\rangle} z_{S'} - \frac{\rho}{\rho+1} z_{S'}
            .
        \end{align*}
        We readily verify that this transformation is a bi-Lipschitz mapping from $G \cup G^{c}$ onto $G^{c}$
        that satisfies the desired mapping properties. 
        It remains to analyze its Jacobian and get explicit estimates for its singular values.
            \frac{ 1 }{ 1 + \rho }  
            \frac{ z_{S'} \otimes h_{z}^{t} }{ \langle h_{z},z_{S'}\rangle }  
            \frac{ 1 }{ 1 + \rho }  
            \frac{ z_{S'} \otimes h_{z}^{t} }{ \langle h_{z},h_{z}\rangle }  
            \frac{ 1 }{ 1 + \rho }  
            \frac{ h_{z} \otimes h_{z}^{t} }{ \langle h_{z},h_{z}\rangle } 
            \frac{ 1 }{ 1 + \rho }  
            \frac{ b_{z} \otimes h_{z}^{t} }{ \langle h_{z},h_{z}\rangle } 
            \frac{ 1 }{ 1 + \rho }  
            \frac{ \vecnorm{ b_{z} } / \vecnorm{ h_{z} } }{ 1 + \rho }  
        The Jacobian acts as the identity over the orthogonal complement of the span of $h_{z}$ and $z_{s'}$.
        Hence, $\tan(\beta) = \vecnorm{ b_{z} } / \vecnorm{ h_{z} }$. 
        Direct computation shows 
            \Jacobian \Phi_{G}(x) \cdot \hat b_{z} = \hat b_{z}
            \Jacobian \Phi_{G}(x) \cdot \hat h_{z} = \frac{ \rho }{ 1 + \rho } \hat h_{z} - \frac{ \vecnorm{ b_{z} } / \vecnorm{ h_{z} } }{ 1 + \rho } \hat b_{z}
        It remains to study the singular values of the matrix 
                 \frac{ \rho }{ 1 + \rho }    & 0 
                -\frac{ \tan(\beta) }{1+\rho} & 1 
            \frac{1}{2(1+\rho)} \sqrt{ (2\rho + 1)^{2} + \tan(\beta)^2 } + \frac{1}{2(1+\rho)} \sqrt{ 1 + \tan(\beta)^2 } 
            \frac{1}{2(1+\rho)} \sqrt{ (2\rho + 1)^{2} + \tan(\beta)^2 } - \frac{1}{2(1+\rho)} \sqrt{ 1 + \tan(\beta)^2 } 
        Notice that 
            \det \Jacobian\Phi = \sigma_{\max}(\Phi,G) \sigma_{\min}(\Phi,G) = \frac{\rho(1+\rho)}{(1+\rho)^2}.
            \frac{1}{2(1+\rho)} \sqrt{ (2\rho + 1)^{2} + (\ell+1)^2 \aspectratio(T)^2 } 
            \frac{1}{2(1+\rho)} \sqrt{               1 + (\ell+1)^2 \aspectratio(T)^2 }
            % \frac{(1+\rho)^2}{\rho(1+\rho)}
            % \frac{1}{2(1+\rho)} 
            \frac{1}{2\rho}
            \sqrt{ (2\rho + 1)^{2} + (\ell+1)^2 \aspectratio(T)^2 } 
            % \frac{(1+\rho)^2}{\rho(1+\rho)}
            % \frac{1}{2(1+\rho)} 
            \frac{1}{2\rho}
            \sqrt{               1 + (\ell+1)^2 \aspectratio(T)^2 }

@@

\begin{theorem}\label{theorem:poincarefriedrichsestimate:exterior:contraction}
    Let $\calT$ be a shellable $n$-dimensional triangulation, and let the domain $\Omega \subseteq \bbR^{n}$ be the interior of the underlying set of $\calT$.
    Let $T_0, T_1, \dots, T_M$ be a shelling of $\calT$.
    Then for any $u \in W^{p}\Alt^{k}(\Omega)$, where $1 \leq p \leq \infty$, 
    there exists $w \in W^{p}\Alt^{k}(\Omega)$ with $\cartan w = \cartan u$ 
    such that 
    \begin{align*}
        \| w \|_{L^{p}(\Omega)}
        \leq 
%         \left( 
%             \Cachttrafo{n}{k}{\ell}(\calT)
            % \Cacht{n}{k}(\calT)
            % \Cachtprime{n}{k}(\calT)^{k} 
            % \Cdetsieb{n}{k}(\calT)^{\frac 1 p} 
%             \Csiebtrafo{n}{k}{\ell}(\calT)
            % \Csieb{n}{k}(\calT)
            % \Csiebprime{n}{k}(\calT)^{k-1} 
            % \Cdetacht{n}{k}(\calT)^{\frac 1 p} 
%         \right)^{M}
        \left( 
        \prod_{m=1}^{M}
            \Cachttrafo{n}{k}{\ell_{m}}{p}(\calT)
            \Csiebtrafo{n}{k}{\ell_{m}}{p}(\calT)
        \right)
        C_{{\PF},k,T_{0},p}
        \| \cartan u \|_{L^{p}(\Omega)}
        ,
    \end{align*}
    where $0 \leq \ell_{m} < n$ is such that $T_{m}$ has $n - \ell$ faces in common with the previous simplices.
\end{theorem}
\begin{proof}\color{blue}
    We first fix some notation. 
    Recall that for any $1 \leq m \leq M$, 
    the sequence $T_0, T_1, \dots, T_{m-1}$ is the shelling of a triangulation of an $n$-dimensional submanifold with boundary, 
    written $X_{m}$, whose interior domain we denote by $\Omega_m$. 
    By Lemma~\ref{lemma:existenceofstar}, adding $T_{m}$ to the triangulation completes a star in $\calT$ around some simplex $S_{m} \in X_{m-1}$, 
    and we let $\Makoto_{m-1} \subseteq X_{m-1}$ be the complement of $T_{m}$ in that newly completed star.

>>>>

        Once again, $h_{z}$ denotes the height of $z_{S'}$ within $G$.
        Here, we let $Q \subseteq G \cap G^{c}$ be the subsimplex 
        that is complementary to the line segment from the origin to $z_{S'}$ in $G$.
        Equivalently, $Q$ is complementary to the line segment from the origin to $-z_{S'}$ in $G^{c}$.
        From the definition of simplices, we now conclude that any $x \in G \cup G^{c}$ 
        has a unique representation
        \begin{align*}
            x = \lambda z_{S'} + \mu x_{Q}, \quad \lambda \in [-1,1], \quad \mu \in [0,1], \quad |\lambda| + \mu \leq 1, \quad x_{Q} \in Q,
        \end{align*}
        Since $\mu x_{Q}$ lies in the hyperplane spanned by the origin and $Q$, we have 
        \begin{align*}
            \lambda = \lambda(x) := \frac{\langle h_{z},x\rangle}{\langle h_{z},z_{S'}\rangle} 
            .
        \end{align*}
        Based on that observation, we define 
        \begin{align*}
            \Phi_{G}(x) 
            &
            := 
            \mu x_{Q} - \frac 1 2 \left( \lambda(x) - 1 \right) z_{S'}
            \\&
            = 
            x - \left( \frac 3 2 \lambda(x) - \frac 1 2 \right) z_{S'}
            = 
            x - \left( \frac 3 2 \frac{\langle h_{z},x\rangle}{\langle h_{z},z_{S'}\rangle} - \frac 1 2 \right) z_{S'}
            .
        \end{align*}
        We readily verify that this transformation is a bi-Lipschitz mapping from $G \cup G^{c}$ onto $G^{c}$
        that satisfies the desired mapping properties. 
        It remains to analyze its Jacobian to get explicit estimates.

@@

            \frac{3}{ 2 \langle h_{z},z_{S'}\rangle }  

@@

            \frac{3}{ 2 \langle h_{z}, h_{z}\rangle } 

@@

            \frac{3}{ 2 } 

@@

            \frac{ 3 \vecnorm{ b_{z} } }{ 2 \vecnorm{ h_{z} } } 

@@

        The Jacobian acts as the identity over the span of $h_{z}$ and $z_{s'}$.

@@

        Hence, $\tan(\beta) = \vecnorm{ b_{z} } / \vecnorm{ h_{z} }$. It remains to study the singular values of the matrix 

@@

                -\frac 1 2             & 0 
                -\frac 3 2 \tan(\beta) & 1 

@@

%             \frac{1}{2} 
%             \left( \sqrt{ \left( 1 + \frac 1 2 \right)^2 + \frac 9 4 \tan(\beta)^2 } + \sqrt{ \left( 1 - \frac 1 2 \right)^2 + \frac 9 4 \tan(\beta)^2 } \right)
%             \frac{1}{2} 
%             \left( \sqrt{ \frac 9 4 + \frac 9 4 \tan(\beta)^2 } + \sqrt{ \frac 1 4 + \frac 9 4 \tan(\beta)^2 } \right)
            \frac{3}{4} \sqrt{ 1 + \tan(\beta)^2 } + \frac{1}{4} \sqrt{ 1 + 9 \tan(\beta)^2 } 

@@

%             \frac{1}{2} 
%             \left( \sqrt{ \left( 1 + \frac 1 2 \right)^2 + \frac 9 4 \tan(\beta)^2 } - \sqrt{ \left( 1 - \frac 1 2 \right)^2 + \frac 9 4 \tan(\beta)^2 } \right)
%             \frac{1}{2} 
%             \left( \sqrt{ \frac 9 4 + \frac 9 4 \tan(\beta)^2 } - \sqrt{ \frac 1 4 + \frac 9 4 \tan(\beta)^2 } \right)
            \frac{3}{4} \sqrt{ 1 + \tan(\beta)^2 } - \frac{1}{4} \sqrt{ 1 + 9 \tan(\beta)^2 } 

@@

            \frac 3 4 \sqrt{ 1 + (\ell+1)^2 \aspectratio(T)^2 } + \frac 1 4 \sqrt{ 1 + 9(\ell+1)^2 \aspectratio(T)^2 }
            1 + \frac{3}{2} (\ell+1) \aspectratio(T) 

@@

            \frac 3 2 \sqrt{ 1 + (\ell+1)^2 \aspectratio(T)^2 } + \frac 1 2 \sqrt{ 1 + 9(\ell+1)^2 \aspectratio(T)^2 }
            2 + 3 (\ell+1) \aspectratio(T) 

@@

        \color{red}Moreover, it is evident that the eigenvalues of the Jacobian are $1$ with multiplicity $n-1$ and $-\tfrac 1 2$ with multiplicity $1$.\color{black}

@@

            \left( 1 + \frac{3}{2} (\ell+1) \aspectratio(T) \right)

@@

            \left( 2 + 3 (\ell+1) \aspectratio(T) \right)

@@

            \left( 1 + \frac 3 2 ( \ell+1 )\aspectratio(\calT) \right)

@@

            \left( 2 + 3 ( \ell+1 )\aspectratio(\calT) \right)

@@

\begin{remark}\label{remark:improved_starreflection}
    The estimates in Proposition~\ref{proposition:starreflection} should be considered as \textit{proof-of-concept} but not as optimal in any sense.
    Some improvements are immediately possible if $\ell=n-1$. 
    Then the reflection $\Xi$ in Lemma~\ref{lemma:volumecomparison} satisfies the same properties as the mapping $\Xi_{1}$,
    mapping the simplex $T$ bijectively onto the $\Makoto$ and being the identity along the common face $S$.
    However, at any point, the singular values $\sigma_1 \geq \dots \geq \sigma_n$ of the Jacobian of $\Xi$ satisfy 
    %     \begin{gather*}
    %         \sigma_1      \leq \aspectratio(\calT) ( 1 + \diameterratio(\calT) ),
    %         \quad 
    %         \sigma_2,\dots,\sigma_{n-1} \leq 1,
    %         \quad 
    %         \sigma^{-1}_n \leq \aspectratio(\calT) ( 1 + \diameterratio(\calT) ),
    %         \\ 
    %         | \det\Jacobian\Xi^{  } |      \leq \aspectratio(\calT) \diameterratio(\calT),
    %         \quad 
    %         | \det\Jacobian\Xi^{-1} |      \leq \aspectratio(\calT) \diameterratio(\calT).
    %     \end{gather*}
    \begin{gather*} 
        | \det\Jacobian\Xi^{  } |      \leq \volumeratio(\calT),
        \\
        \sigma_{1}
        \leq 
        \frac{1}{2} 
        \sqrt{ \left( \diameterratio(\calT) \aspectratio(\calT) + 1 \right)^{2} + \aspectratio(\calT)^{2} }
        +
        \frac{1}{2} 
        \sqrt{ \left( \diameterratio(\calT) \aspectratio(\calT) - 1 \right)^{2} + \aspectratio(\calT)^{2} }
        ,
        \\
        \sigma_2,\dots,\sigma_{n-1},\sigma_{n} \leq 1.
    \end{gather*}
    In particular,
    \begin{align*}
        \sigma_{1}\cdots\sigma_{k} | \det\Jacobian\Xi_{2} |^{-\frac 1 p}
        \leq 
        \left( 
            \frac{1}{2} 
            \sqrt{ \left( \diameterratio(\calT) \aspectratio(\calT) + 1 \right)^{2} + \aspectratio(\calT)^{2} }
            +
            \frac{1}{2} 
            \sqrt{ \left( \diameterratio(\calT) \aspectratio(\calT) - 1 \right)^{2} + \aspectratio(\calT)^{2} }
        \right)
        \volumeratio(\calT)^{\frac 1 p}
        .
    \end{align*}
    These estimates improve over the ones in Proposition~\ref{proposition:starreflection} when the reflection is over a single face.
    We believe that better estimates can be computed from the geometric data also in the other cases.
\end{remark}

@@

\begin{theorem}\label{theorem:poincarefriedrichsestimate:exterior:contraction}
    Let $\calT$ be a shellable $n$-dimensional triangulation, and let the domain $\Omega \subseteq \bbR^{n}$ be the interior of the underlying set of $\calT$.
    Let $T_0, T_1, \dots, T_M$ be a shelling of $\calT$.
    Then for any $u \in W^{p}\Alt^{k}(\Omega)$, where $1 \leq p \leq \infty$, 
    there exists $w \in W^{p}\Alt^{k}(\Omega)$ with $\cartan w = \cartan u$ 
    such that 
    \begin{align*}
        \| w \|_{L^{p}(\Omega)}
        \leq 
%         \left( 
%             \Cachttrafo{n}{k}{\ell}(\calT)
            % \Cacht{n}{k}(\calT)
            % \Cachtprime{n}{k}(\calT)^{k} 
            % \Cdetsieb{n}{k}(\calT)^{\frac 1 p} 
%             \Csiebtrafo{n}{k}{\ell}(\calT)
            % \Csieb{n}{k}(\calT)
            % \Csiebprime{n}{k}(\calT)^{k-1} 
            % \Cdetacht{n}{k}(\calT)^{\frac 1 p} 
%         \right)^{M}
        \left( 
        \prod_{m=1}^{M}
            \Cachttrafo{n}{k+1}{\ell_{m}}{p}(\calT)
            \Csiebtrafo{n}{k  }{\ell_{m}}{p}(\calT)
        \right)
        C_{{\PF},k,T_{0},p}
        \| \cartan u \|_{L^{p}(\Omega)}
        ,
    \end{align*}
    where $0 \leq \ell_{m} < n$ is such that $T_{m}$ has $n - \ell$ faces in common with the previous simplices.
\end{theorem}
\begin{proof}\color{blue}
    We first fix some notation. 
    Recall that for any $1 \leq m \leq M$, 
    the sequence $T_0, T_1, \dots, T_{m-1}$ is the shelling of a triangulation of an $n$-dimensional submanifold with boundary, 
    written $X_{m}$, whose interior domain we denote by $\Omega_m$. 
    By Lemma~\ref{lemma:existenceofstar}, adding $T_{m}$ to the triangulation completes a star in $\calT$ around some simplex $S_{m} \in X_{m-1}$, 
    and we let $\Makoto_{m-1} \subseteq X_{m-1}$ be the complement of $T_{m}$ in that newly completed star.
